Python as a machine learning language: experiences from the scikit-learn project

### 2013-05-03 paper.tex
repetitive "at the time of writing"

The scikit-learn project started in 2009 and has since been developed
by a team largely consisting of scientists
(both from computer science and other fields).
Its popularity can be gauged from various sources:
% TODO: list volume on the mailing list, number of contributors,
% number of issues opened and closed, number of forks, number of surveys filled in.
at the time of writing,
the popular programmer's Q~\&{}A site StackOverflow\footnote{
  \url{http://stackoverflow.com/questions/tagged/scikit-learn}}
% update the following figure when paper is finalized
lists 322 scikit-learn-related questions.
At the time of writing,  % ddaa494c116e3c16bf032003c5cccbed851733d2
version control logs for the development version of scikit-learn
show 183 contributors to the project's source code and documentation
(after manual deduplication).

>>>>

The scikit-learn project started in 2009 and has since been developed
by a team largely consisting of scientists
(both from computer science and other fields).
Its popularity can be gauged from various sources:
% TODO: list volume on the mailing list, number of contributors,
% number of issues opened and closed, number of forks, number of surveys filled in.
at the time of writing,
the popular programmer's Q~\&{}A site StackOverflow\footnote{
  \url{http://stackoverflow.com/questions/tagged/scikit-learn}}
% update the following figure when paper is finalized
lists 322 scikit-learn-related questions.
The version control logs for the development version of scikit-learn
% ddaa494c116e3c16bf032003c5cccbed851733d2
show 183 contributors to the project's source code and documentation
(after manual deduplication).
